---
title: "Day1_Afternoon_Interactive"
author: "Connor Flynn"
date: "8/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#library(tidyverse)

```

### Logs and Exponents in R
Some examples of using `log()` function and `exp()` **function** in R

```{r}
#Examples of logarithms

log(4)

#Examples of exponents
exp(5)

#A test of a log()
log(exp(1))
```
### Creating sequences of values

?seq

```{r}
#A sequence from 1 20, by 1

ex_1 <- seq(from = 1, to = 20, by =1)

#Vector from 0 to 40 by increments of 0.2
ex_3 <- seq(from = 0, to = 40, by  =0.2)

#Vector from 1 to 5000 by increments of 10
ex_4 <- seq(from = 1, to = 5000, by = 10)
```

###Create a function for logistic growth
Given the carrying capacity, initial population, the growth rate, and time, use the logistic growth model to estimate the population at that time.

```{r}
pop_logisitc <- function(capacity, initial_pop, growth_rate, time_year){
  
  capacity/ (1+((capacity-initial_pop)/initial_pop)*exp(-growth_rate * time_year))
  
}

pop_logisitc(capacity = 2580, initial_pop = 230, growth_rate = 0.32, time_year = 2.4)
```

```{r}
#Create a vector of times from 0 to 20 by increments of 0.5

time_vec <- seq(from = 0, to = 20, by = 0.5)
```

Now let's estimate the population over that range of times, given capacity = 2,580, initial population = 230, rate = 0.32

```{r}
chipmunk_pop <- pop_logisitc(capacity = 2580, initial_pop = 230, growth_rate = 0.32, time_year = time_vec)
```

### Create a data frame and plot chipmunk population over time

```{r}
chipmunk_df <- data.frame(time_vec, chipmunk_pop)

```


###Create a bare minimum ggplot graph:

```{r}

#ggplot(data=chipmunk_df, aes(x = time_vec, y = chipmunk_pop)) + 
#  geom_point()
```

